Four decades of water quality change in the upper San Francisco Estuary\footnote{Version: Thu Feb 9 09:38:49 2017 -0600, \href{https://github.com/fawda123/sftrends_manu/commit/dc55a82ecaa6c7579c80e824377410a6b61dc53f}{dc55a82ecaa6c7579c80e824377410a6b61dc53f}}

### 2017-05-02 sftrends_manu.tex
david to last

\author{Marcus W. Beck}
\affiliation{USEPA National Health and Environmental Effects Research Laboratory, Gulf Ecology Division, Gulf Breeze, FL}
\email{beck.marcus@epa.gov}
\phone{+1 (850)9342480}
\fax{+1 (850)9342401}
\author{David B. Senn}
\author{Thomas W. Jabusch}
\author{Philip R. Trowbridge}
\affiliation{San Francisco Estuary Institute, Richmond, CA}

\title[Water quality change in the upper SFE]{Four decades of water quality change in the upper San Francisco Estuary\footnote{Version: Wed Mar 15 17:49:38 2017 -0500, \href{https://github.com/fawda123/sftrends_manu/commit/835c0b4e439bcdbb0228b9b56799bfb4764b7d97}{835c0b4e439bcdbb0228b9b56799bfb4764b7d97}\newline The views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the U.S. Environmental Protection Agency.}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\linenumbers

>>>>

\author{Marcus W. Beck}
\affiliation{USEPA National Health and Environmental Effects Research Laboratory, Gulf Ecology Division, Gulf Breeze, FL}
\email{beck.marcus@epa.gov}
\phone{+1 (850)9342480}
\fax{+1 (850)9342401}
\author{Thomas W. Jabusch}
\author{Philip R. Trowbridge}
\author{David B. Senn}
\affiliation{San Francisco Estuary Institute, Richmond, CA}

\title[Water quality change in the upper SFE]{Four decades of water quality change in the upper San Francisco Estuary\footnote{Version: Tue May 2 08:37:44 2017 -0500, \href{https://github.com/fawda123/sftrends_manu/commit/2a1fcbeba412e8ea16c8fea91f775c46617d667d}{2a1fcbeba412e8ea16c8fea91f775c46617d667d}\newline The views expressed in this paper are those of the authors and do not necessarily reflect the views or policies of the U.S. Environmental Protection Agency.}}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\linenumbers
